%% Junhyeong Lee -- Curriculum Vitae
%% Compile with: pdflatex or xelatex

\documentclass[11pt, a4paper]{article}

%% -- Packages ----------------------------------------------------------
\usepackage[top=0.85in, bottom=0.85in, left=0.9in, right=0.9in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{etaremune}
\usepackage{fancyhdr}
\usepackage{changepage}

%% -- Hyperref ----------------------------------------------------------
\hypersetup{colorlinks=true, urlcolor=blue, linkcolor=black}

%% -- Page style --------------------------------------------------------
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{\small\thepage}
\fancyfoot[C]{\small Junhyeong Lee}
\fancyfoot[R]{\small Daejeon, South Korea $|$ jhl8831@kaist.ac.kr}

\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}

%% -- Section label width -----------------------------------------------
\newlength{\seclabelwd}
\setlength{\seclabelwd}{1.25in}

%% -- Section environment: label left, content right, same row ---------
\newenvironment{cvsec}[1]{%
  \par\vspace{0.9em}%
  \noindent{\large\bfseries #1}\par\nobreak%
  \vspace{2pt}%
  \noindent\rule{\linewidth}{0.4pt}\par\nobreak%
  \vspace{3pt}%
  \noindent%
}{%
  \vspace{2pt}%
}

%% -- List styles -------------------------------------------------------
%% etaremune: reversed numbering for publications (newest = highest number)
\setlist[etaremune]{
  leftmargin = 2em,
  itemsep    = 5pt,
  parsep     = 0pt,
  topsep     = 0pt,
  partopsep  = 0pt
}

%% publist: ascending numbering for patents, conferences, under review
\newlist{publist}{enumerate}{1}
\setlist[publist]{
  leftmargin = 2em,
  label      = \arabic*.,
  itemsep    = 5pt,
  parsep     = 0pt,
  topsep     = 0pt,
  partopsep  = 0pt
}

\newlist{cvbullet}{itemize}{1}
\setlist[cvbullet]{
  leftmargin = 1.5em,
  label      = $\bullet$,
  itemsep    = 1pt,
  parsep     = 0pt,
  topsep     = 2pt
}

%% -- Entry helper: bold title, right-aligned date, detail below -------
\newcommand{\entry}[3]{%
  \noindent\textbf{#1}\hfill\mbox{#2}\par%
  \ifx&#3&\else\noindent #3\par\fi%
  \vspace{4pt}%
}

%% ======================================================================
\begin{document}

%% -- Header ------------------------------------------------------------
{\huge\bfseries Junhyeong Lee}

\vspace{0.3em}
\noindent\rule{\linewidth}{0.8pt}
\vspace{0.2em}

\noindent
Department of Mechanical Engineering,
Korea Advanced Institute of Science and Technology (KAIST) \\
Email: \href{mailto:jhl8831@kaist.ac.kr}{jhl8831@kaist.ac.kr} \quad
Homepage: \href{https://junhyeong1025.github.io}{junhyeong1025.github.io}

\vspace{0.3em}

%% -- Research Interests -----------------------------------------------
\begin{cvsec}{Research Interests}
Artificial intelligence for inverse design \quad$\cdot$\quad
Artificial intelligence for manufacturing \quad$\cdot$\quad
Data-driven optimization \quad$\cdot$\quad
Large Language Models
\end{cvsec}

%% -- Education --------------------------------------------------------
\begin{cvsec}{Education \& Experience}

\entry{Postdoctoral Fellow}{Feb.~2026 -- Present}{%
  PRISM-AI Center (InnoCORE) \& AiM$^4$ Lab,
  Korea Advanced Institute of Science and Technology (KAIST), S.~Korea \\
  Advisor: Prof.\ Seunghwa Ryu
}

\entry{Ph.D.\ in Mechanical Engineering}{Sep.~2022 -- Feb.~2026}{%
  Korea Advanced Institute of Science and Technology (KAIST), S.~Korea \\
  Advisor: Prof.\ Seunghwa Ryu
}

\entry{Research Assistant}{Mar.~2022 -- Aug.~2022}{%
  Department of Mechanical Engineering, KAIST, S.~Korea \\
  Advisor: Prof.\ Seunghwa Ryu
}

\entry{M.S.\ in Mechanical Engineering}{Mar.~2020 -- Feb.~2022}{%
  Korea Advanced Institute of Science and Technology (KAIST), S.~Korea \\
  Advisor: Prof.\ Seunghwa Ryu
}

\entry{B.Eng.\ in Convergence Engineering, \textit{Summa Cum Laude}}{Mar.~2015 -- Feb.~2019}{%
  Daegu Gyeongbuk Institute of Science and Technology (DGIST), S.~Korea
}

\end{cvsec}

%% -- Publications -----------------------------------------------------
%% Total published: 13 papers. Reversed numbering: newest = 13, oldest = 1.
\begin{cvsec}{Publications}

\textit{$^+$Equal contribution \quad $^*$Corresponding author}

\vspace{3pt}
\textbf{2026}
\begin{etaremune}[start=13]

\item Lee,~S., \textbf{Lee,~J.}, Park,~D., Lee,~S., Lee,~K.$^*$, Kim,~H.$^*$, \& Ryu,~S.$^*$
``Reducing False Negatives in Gastroesophageal Reflux Disease Diagnosis Through Multi-Feature Anomaly Detection of pH-Impedance Signals.''
\textbf{npj Digital Medicine}, In press.

\item \textbf{Lee,~J.}$^+$, Kim,~J.$^+$, Kee,~S.$^+$, Yu,~J., \& Ryu,~S.$^*$
``Federated Learning Framework for Data-Sovereign Quality Prediction in Injection Molding.''
\textbf{International Journal of Precision Engineering and Manufacturing}, In press.
\href{https://doi.org/10.1007/s12541-026-01546-0}{10.1007/s12541-026-01546-0}

\end{etaremune}

\vspace{3pt}
\textbf{2025}
\begin{etaremune}[start=11]

\item \textbf{Lee,~J.}$^+$, Kim,~J.$^+$, Kim,~H.$^+$, Lee,~I., \& Ryu,~S.$^*$
``IM-Chat: A Multi-agent LLM-based Framework for Knowledge Transfer in Injection Molding Industry.''
\textbf{Journal of Manufacturing Systems} (IF:~14.2, JCR Top~0.7\%), In press.
\href{https://doi.org/10.1016/j.jmsy.2025.11.007}{10.1016/j.jmsy.2025.11.007}

\item Lee,~H.$^+$, Moon,~H.$^+$, \textbf{Lee,~J.}$^+$, \& Ryu,~S.$^*$
``Toward Knowledge-Guided AI for Inverse Design in Manufacturing: A Perspective on Domain, Physics, and Human-AI Synergy.''
\textbf{Advanced Intelligent Discovery}, e202500107.
\href{https://doi.org/10.1002/aidi.202500107}{10.1002/aidi.202500107}

\item Kang,~H.$^+$, \textbf{Lee,~J.}$^+$, Lee,~S., Jeon,~J., Mun,~C., Yang,~J., Kwon,~H., Lee,~I., Kim,~S., Lim,~E., Jung,~J., Jung,~Y.$^*$, Park,~S.$^*$, Ryu,~S.$^*$, \& Kang,~T.$^*$
``Interpretability-Driven Deep Learning for SERS-based Classification of Respiratory Viruses.''
\textbf{Biosensors and Bioelectronics}, 117891 (IF:~10.5, JCR Top~3.2\%).
\href{https://doi.org/10.1016/j.bios.2025.117891}{10.1016/j.bios.2025.117891}

\item Yoon,~J.$^+$, \textbf{Lee,~J.}$^+$, Ryu,~S.$^*$, \& Park,~J.$^*$
``Enhanced Energy Harvesting in Rotary Triboelectric Nanogenerators via Gaussian Process Regression-Based Bayesian Optimization.''
\textbf{Nano Energy}, 135, 110653 (IF:~17.1, JCR Top~7.8\%).
\href{https://doi.org/10.1016/j.nanoen.2025.110653}{10.1016/j.nanoen.2025.110653}

\item Moon,~H., \textbf{Lee,~J.}, Yu,~J., \& Ryu,~S.$^*$
``Physics-Informed AI for Material Characterization: A Perspective on Data-Efficient Discovery through Physics-Informed Neural Networks.''
\textbf{International Journal of AI for Materials and Design}, 2(4).
\href{https://doi.org/10.36922/IJAMD025440043}{10.36922/IJAMD025440043}

\end{etaremune}

\vspace{3pt}
\textbf{2024}
\begin{etaremune}[start=6]

\item \textbf{Lee,~J.}, Park,~K., Park,~K., Kim,~Y., Kim,~J.$^*$, \& Ryu,~S.$^*$
``Electrode Placement Optimization for Electrical Impedance Tomography using Active Learning.''
\textbf{Advanced Engineering Materials}, 26(11), 2301865.
\href{https://doi.org/10.1002/adem.202301865}{10.1002/adem.202301865}

\item Kang,~H.$^+$, \textbf{Lee,~J.}$^+$, Moon,~J.$^+$, Lee,~T.$^+$, Lim,~E., Jung,~J., Jung,~Y., Lee,~S., Lee,~K.$^*$, Ryu,~S.$^*$, \& Kang,~T.$^*$
``Multiplex Detection of Foodborne Pathogens using 3D Nanostructure Swab and Deep Learning-based Classification Raman Spectra.''
\textbf{Small}, 20(35), 2308317 (IF:~13.0, JCR Top~10.6\%). (front cover)
\href{https://doi.org/10.1002/smll.202308317}{10.1002/smll.202308317}

\end{etaremune}

\vspace{3pt}
\textbf{2023}
\begin{etaremune}[start=4]

\item \textbf{Lee,~J.}, Park,~D., Lee,~M., Lee,~H., Park,~K., Lee,~I., \& Ryu,~S.$^*$
``Machine learning-based inverse design methods considering data characteristics and design space size in materials design and manufacturing: a review.''
\textbf{Materials Horizons}, 10, 5436--5456 (IF:~13.3, JCR Top~9.8\%).
\href{https://doi.org/10.1039/D3MH00039G}{10.1039/D3MH00039G}

\end{etaremune}

\vspace{3pt}
\textbf{2022}
\begin{etaremune}[start=3]

\item Yoon,~J.$^+$, \textbf{Lee,~J.}$^+$, Kim,~G., Ryu,~S.$^*$, \& Park,~J.$^*$
``Deep neural network-based structural health monitoring technique for real-time crack detection and localization using strain gauge sensors.''
\textbf{Scientific Reports}, 12(1), 20204.
\href{https://doi.org/10.1038/s41598-022-24269-4}{10.1038/s41598-022-24269-4}

\end{etaremune}

\vspace{3pt}
\textbf{2021}
\begin{etaremune}[start=2]

\item Park,~K., \textbf{Lee,~J.}, \& Ryu,~S.$^*$
``Damage detection of composite materials via IR thermography and electrical resistance measurement: A review.''
\textbf{Structural Engineering and Mechanics}, 80(5), 563--583.
\href{https://doi.org/10.12989/sem.2021.80.5.563}{10.12989/sem.2021.80.5.563}

\end{etaremune}

\vspace{3pt}
\textbf{2020}
\begin{etaremune}[start=1]

\item Lim,~S.~H.$^+$, Sohn,~S.~W.$^+$, Lee,~H., Choi,~D., Jang,~E., Kim,~M., \textbf{Lee,~J.}, \& Park,~S.$^*$
``Analysis and evaluation of path planning algorithms for autonomous driving of electromagnetically actuated microrobot.''
\textbf{International Journal of Control, Automation and Systems}, 18, 2943--2954.
\href{https://doi.org/10.1007/s12555-019-0637-9}{10.1007/s12555-019-0637-9}

\end{etaremune}

\vspace{3pt}
\textbf{Under Review / In Preparation}
\begin{publist}

\item Yu,~J.$^+$, Byun,~J.$^+$, Moon,~H., \textbf{Lee,~J.}, \& Ryu,~S.$^*$
``Dual-Constrained Diffusion Model for Nonlinear Microstructure Inverse Design with Direct Evaluation.'' Under review.

\item Demeke,~W.$^+$, \textbf{Lee,~J.}$^+$, Lee,~I.$^+$, Ryu,~B.$^*$, \& Ryu,~S.$^*$
``A Comprehensive Review of Thermoelectric Power Generators: Advances in Material Discovery, Structural Optimization for Performance Enhancement, and Service Life Stability.'' Under review.

\item Cho,~H., Yu,~J., Moon,~H., Yoon,~J., \textbf{Lee,~J.}, Kim,~G., Park,~J., \& Ryu,~S.$^*$
``Real-Time Structural Health Monitoring with Bayesian Neural Networks: Distinguishing Aleatoric and Epistemic Uncertainty for Digital Twin Frameworks.'' Under review.
[\href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=5549564}{SSRN}]

\item Lee,~I.$^+$, \textbf{Lee,~J.}$^+$, Park,~J., Lim,~K.$^*$, \& Ryu,~S.$^*$
``Enhancing LLM-based Conditional Material Generation for Double Perovskite through Multi-Agent Feedback and Domain Knowledge.'' In preparation.
[\href{https://arxiv.org/abs/2511.22307}{arXiv:2511.22307}]

\end{publist}

\end{cvsec}

%% -- Patents ----------------------------------------------------------
\begin{cvsec}{Patents}

\begin{publist}

\item Kim,~J., \textbf{Lee,~J.}, Kim,~H., Lee,~I., Ryu,~S., Nam,~K., \& Yoon,~S. (2025).
``Knowledge Transfer Device and Method using an Agent Based on a Large Language Model.''
Filed (KR 10-2025-0145843).

\item Ryu,~S., \textbf{Lee,~J.}, \& Park,~K. (2023).
``Method and Apparatus for Optimization of Cathode Material Design Multi-objective Bayesian Optimization.''
Filed (KR 10-2023-0172701).

\end{publist}

\end{cvsec}

%% -- Conferences ------------------------------------------------------
\begin{cvsec}{Conferences}

\begin{publist}

\item Choi,~D., Jang,~E., Kim,~M., \textbf{Lee,~J.}, Lim,~S., Sohn,~S., Lee,~H., \& Park,~S.$^*$ (2018).
``Analysis of Path Planning Algorithm for Autonomous Control of Electromagnetically Actuated Microrobot.''
\textbf{SMIT2018-IBEC2018 Joint Conference} (Poster).

\item \textbf{Lee,~J.}, \& Ryu,~S.$^*$ (2021).
``Data-Driven Electrode Placement Optimization for Crack Sensing of Carbon-based Composites using Electrical Resistance Tomography.''
\textbf{KSME CAE \& Applied Mechanics Conference} (Oral).

\item \textbf{Lee,~J.}, Lee,~H., \& Ryu,~S.$^*$ (2022).
``Electrode Placement Optimization for Electrical Resistance Tomography using Transfer Learning.''
\textbf{KSME CAE \& Applied Mechanics Conference} (Oral).

\item \textbf{Lee,~J.}, \& Ryu,~S.$^*$ (2022).
``Deep Learning-based Electrode Placement Optimization for Crack Sensing of Carbon-based Composites using Electrode Resistance Tomography.''
\textbf{GRC Additive Manufacturing of Soft Materials} (Poster).

\item \textbf{Lee,~J.}$^+$, Yoon,~J.$^+$, Kim,~G., Park,~J.$^*$, \& Ryu,~S.$^*$ (2023).
``A Deep Learning Approach for Crack Sensing in Structural Health Monitoring using Strain Gauge Sensors.''
\textbf{COSEIK} (Oral).

\item \textbf{Lee,~J.}$^+$, Yoon,~J.$^+$, Kim,~G., Park,~J.$^*$, \& Ryu,~S.$^*$ (2023).
``Real-time Crack Localization using Strain Gauge Sensors with Deep Learning.''
\textbf{KSME CAE \& Applied Mechanics Conference} (Oral).

\item \textbf{Lee,~J.}$^+$, Park,~D., Lee,~M., Park,~K., Lee,~H., Lee,~I., Lee,~I., \& Ryu,~S.$^*$ (2024).
``Review of Machine Learning-based Inverse Design Methods in Materials Design and Manufacturing.''
\textbf{KSME CAE \& Applied Mechanics Conference} (Poster).

\item Kang,~H.$^+$, \textbf{Lee,~J.}$^+$, Moon,~J.$^+$, Lee,~T.$^+$, Lim,~E., Jung,~J., Jung,~Y., Lee,~S., Lee,~K.$^*$, Ryu,~S.$^*$, \& Kang,~T.$^*$ (2024).
``Detection of Multiple Foodborne Pathogens Utilizing a Three-dimensional Nanostructure Swab and Deep Learning-based Analysis of Raman Spectra.''
\textbf{Nano Korea} (Oral).

\item Kang,~H.$^+$, \textbf{Lee,~J.}$^+$, Moon,~J.$^+$, Lee,~T.$^+$, Lim,~E., Jung,~J., Jung,~Y., Lee,~S., Lee,~K.$^*$, Ryu,~S.$^*$, \& Kang,~T.$^*$ (2024).
``3D Nanostructure Swab and Deep Learning Analysis of Raman Spectra for Detection of Multiple Foodborne Pathogens.''
\textbf{KSME Conference} (Oral).

\item Lee,~I., \textbf{Lee,~J.}, \& Ryu,~S.$^*$ (2025).
``Multi-Agent Argumentative LLM Framework for Conditional Exploration of Double-Perovskite Materials.''
\textbf{Spring Conference of the Korean Institute of Metals and Materials} (Oral).

\item \textbf{Lee,~J.}$^+$, Kim,~J.$^+$, Kim,~H.$^+$, Lee,~I., Park,~J., \& Ryu,~S.$^*$ (2025).
``Enhancing Knowledge Transfer in Injection Molding Through a Multi-Agent LLM Framework.''
\textbf{KSME CAE \& Applied Mechanics Conference} (Oral).

\item \textbf{Lee,~J.}, Kim,~J., Kim,~H., Lee,~I., Choi,~H., \& Ryu,~S.$^*$ (2026).
``LLM-based Knowledge Transfer System for Injection Molding: Implementation and Performance Enhancement.''
\textbf{KSME CAE \& Applied Mechanics Conference} (Oral).

\end{publist}

\end{cvsec}

%% -- Honors & Awards --------------------------------------------------
\begin{cvsec}{Honors \& Awards}

\entry{Excellent Dissertation Award, KSME Headquarters}{2026}{}
\entry{Outstanding Paper Award, KSME CAE \& Applied Mechanics Division}{2026}{}
\entry{Woo-Deok Future Scholar (우덕미래장학생), Woo-Deok Foundation}{2025}{}
\entry{Outstanding Paper Award, KSME CAE \& Applied Mechanics Division}{2025}{}

\entry{DGIST Presidential Fellowship}{2016--2019}{%
  \begin{cvbullet}
    \item Placed on the Dean's list.
    \item \$10K expenses for Undergraduate Group Research Program
    \item \$20K financial support for overseas lab experience
  \end{cvbullet}
}

\entry{Dean's List, DGIST}{2015}{%
  \begin{cvbullet}
    \item Included in the top 5 excellent students ranking in each semester
    \item \$2.5K financial support for undergraduate study
  \end{cvbullet}
}

\end{cvsec}

%% -- Projects ---------------------------------------------------------
\begin{cvsec}{Projects}

\entry{InnoCORE Project, MSIT Korea}{2025--Present}{%
  \begin{cvbullet}
    \item National flagship program ($\sim$\$25M USD over 4.5 years) to advance AI-driven manufacturing across KAIST, GIST, DGIST, and UNIST.
    \item Led proposal development and conceptual design of an LLM-based autonomous manufacturing framework.
    \item Developing LLM-driven methods for materials design, structural optimization, and process parameter tuning.
  \end{cvbullet}
}

\entry{National Agenda Basic Research Program, MSIT Korea}{2025--Present}{%
  \begin{cvbullet}
    \item Three-year project ($\sim$\$150K USD/year) developing domain-specialized LLMs for advanced manufacturing productivity.
    \item Contributing to core LLM frameworks enabling intelligent, domain-aware automation in smart manufacturing.
  \end{cvbullet}
}

\end{cvsec}

%% -- Teaching ---------------------------------------------------------
\begin{cvsec}{Teaching \& Leadership}

\entry{AiM$^4$ Lab Student Representative, KAIST}{2024}{%
  \begin{cvbullet}
    \item Coordinated research activities, organized internal seminars, managed lab resources
  \end{cvbullet}
}

\entry{Teaching Assistant, KAIST}{2022--2025}{%
  \begin{cvbullet}
    \item ME567: Introduction to Statistical Thermodynamics (2022)
    \item ME231: Solid Mechanics (2023, 2025)
    \item ME639: Elasticity \& Micromechanics (2023)
    \item ME211: Thermodynamics (2024)
    \item ME491B: Statistical Data Analysis (2024)
    \item ME221: Fluid Mechanics (2024, 2025)
  \end{cvbullet}
}

\entry{Teaching Assistant, DGIST}{2019}{%
  \begin{cvbullet}
    \item SE201b: Linear Algebra (2019)
  \end{cvbullet}
}

\end{cvsec}

%% -- Skills -----------------------------------------------------------
\begin{cvsec}{Skills}

\textbf{Simulation / Coding:}
COMSOL Multiphysics, ABAQUS, Fe-safe, HyperMesh, ADINA, EIDORS, MATLAB, Python

\smallskip
\textbf{Data-Driven Design:}
Generative modeling, surrogate modeling \& optimization, Bayesian optimization

\smallskip
\textbf{Large Language Model:}
Multi-agent orchestration, RAG (retrieval-augmented generation), tool-calling

\smallskip
\textbf{Languages:} Korean (native), English (advanced)

\end{cvsec}

%% -- References -------------------------------------------------------
\begin{cvsec}{References}

\textbf{Prof.\ Seunghwa Ryu} \quad
Department of Mechanical Engineering, KAIST \quad
\href{mailto:ryush@kaist.ac.kr}{ryush@kaist.ac.kr}

\smallskip
\textbf{Prof.\ Ikjin Lee} \quad
Department of Mechanical Engineering, KAIST \quad
\href{mailto:ikjin.lee@kaist.ac.kr}{ikjin.lee@kaist.ac.kr}

\smallskip
\textbf{Prof.\ Jinhyoung Park} \quad
School of Mechatronics Engineering, Korea University of Technology and Education \quad
\href{mailto:jhpark98@koreatech.ac.kr}{jhpark98@koreatech.ac.kr}

\end{cvsec}

\end{document}
